Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-03 ms.tex
Added Bayesion Information Values.

We have confirmed with a subset of the authors of \citet{zehavi_etal11} 
that the number of MCMC samples they included in their analysis was 
insufficient in a number of cases and that this can lead to a significant underestimation of the uncertainties 
on the inferred parameters, especially $\log (M_{\rm min})$ and $\sigma_{\log M}$ 
(Z. Zheng \& I. Zehavi, Private Communication). The analysis of \citet{zehavi_etal11} 
used $10^4$ samples, whereas we find several $\times 10^6$ samples are often necessary for convergence. 
Additionally, we have recreated qualitatively similar behavior by considering only small subsets of all of our 
full MCMC chains. Consequently, insufficient sampling of the posterior seems to be the likely resolution 
of the discrepancies between our work and that of \citet{zehavi_etal11}.

@@

Table~\ref{table:parameters} and Figures~\ref{fig:Mr19ABtriangle}-\ref{fig:Mr21triangle} 
all make several simple, generic points. Introducing additional parameter 
freedom associated with galaxy assembly bias generally increases the viable parameter 
space, even for the subset of standard HOD parameters. This is exactly what is 
expected from the introduction of additional parameter freedom.

Focusing attention on the parameters describing galaxy assembly bias, it is 
evident that these parameters are often quite poorly constrained by galaxy 
clustering data. This implies that galaxy clustering of the precision of SDSS DR7 
measurements cannot rule out, or strongly restrict galaxy assembly bias in most 
cases.

Beyond those generic conclusions, a few specific cases of worthy of further examination. 
Consider the $M_r < -20$ sample. The inferred value of $A_{\rm cen} > 0.28$ at 99\% 
confidence. In this case the data strongly prefer $A_{\rm cen} > 0$ and thus strongly prefer 
galaxies to reside in halos of larger concentration at fixed halo mass.

Changes in Bayesian Information Criterion, for inclusion in some sort of table. Strong evidence 
is usually considered to be a difference $>5$.

Delta BIC 19: 4.37

Delta BIC 19.5: 0.26

Delta BIC 20: 4.56

Delta BIC 20.5: 1.33

Delta BIC 21: -0.54

>>>>

We have confirmed with a subset of the authors of \citet{zehavi_etal11} 
that the number of MCMC samples they included in their analysis was 
insufficient in a number of cases and that this can lead to a significant underestimation of the uncertainties 
on the inferred parameters, especially $\log (M_{\rm min})$ and $\sigma_{\log M}$ 
(Z. Zheng \& I. Zehavi, Private Communication). The analysis of \citet{zehavi_etal11} 
used $10^4$ samples, whereas we find several $\times 10^6$ samples are often necessary for convergence. 
Additionally, we have recreated qualitatively similar behavior by considering only small subsets of our 
full MCMC chains. Consequently, insufficient sampling of the posterior seems to be the likely resolution 
of the discrepancies between our work and that of \citet{zehavi_etal11}.

@@

Table~\ref{table:parameters} and Figures~\ref{fig:Mr19ABtriangle}-\ref{fig:Mr21triangle} 
all make several simple, generic points. Introducing additional parameter 
freedom associated with galaxy assembly bias generally increases the viable parameter 
space, even for the subset of standard HOD parameters. Constraints on the 
standard HOD parameters are generally less restrictive. This is exactly what is 
expected from the introduction of additional parameter freedom.

Focusing attention on the parameters describing galaxy assembly bias, it is 
evident that these parameters are often quite poorly constrained by galaxy 
clustering data. This is important as it implies that galaxy clustering of the precision 
of SDSS DR7 measurements cannot rule out, or strongly restrict galaxy assembly 
bias in many cases. Nonetheless, it is apparent that the presence of assembly bias 
can alter the inferred HOD, or more generally, the inferred relationship between 
galaxies and halo mass. This is most evident for the $M_r < -20$ threshold sample, 
for which there are significant differences in the inferred values of all baseline HOD 
parameters between models with and without galaxy assembly bias. Other threshold 
samples exhibit significant changes particularly for $\alpha$, and to a lesser degree 
for $\log (M_{\rm min})$ and $\sigma_{\log M}$.

Beyond those generic conclusions, a few specific cases are worthy of further examination. 
Consider the $M_r < -20$ sample. The inferred value of $A_{\rm cen} > 0.28$ at 99\% 
confidence. In this case the data strongly prefer $A_{\rm cen} > 0$ and thus strongly prefer 
galaxies to reside in halos of larger concentration at fixed halo mass. This particular threshold 
sample is the most significant outlier in this regard. Nevertheless, there are hints of assembly 
bias in other samples. Satellite galaxies show a marginal preference for occupying halos of 
higher concentration in the $M_r < -19$ threshold sample. The $M_r < -19$ sample exhibits 
weak preference for a positive correlation of galaxy occupation with halo concentration at fixed 
mass for both satellite galaxies and central galaxies. Continuing upward with luminosity, 
the $M_r < -20.5$ sample exhibits a significant preference for central galaxy assembly bias. 
Lastly, there is no preference for either central galaxy or satellite galaxy assembly bias 
for the $M_r < -21$ threshold sample, for which both $A_{\mathrm{cen}}$ and $A_{\mathrm{sat}}$ 
are consistent with zero will within 1$\sigma$. These data suggest that assembly bias 
may be present in the real universe.

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{table}
\begin{center}
{\renewcommand{\arraystretch}{1.3}
\renewcommand{\tabcolsep}{0.2cm}
\begin{tabular}{c c}
\hline 
\hline
$M_r$ Threshold & $\Delta \mathrm{BIC}$ \\ 
\hline
-21 & -0.54 \\
-20.5 & 1.33 \\
-20 & 4.56\\
-19.5 & 0.26\\
-19 & 4.37\\
\hline
\end{tabular}
\medskip
\caption{
Change to the Bayesian Information Criterion, $\Delta \mathrm{BIC}$, 
after introducing additional parametric freedom to accommodate galaxy 
assembly bias. Sign convention is such that positive values favor models including 
assembly bias, negative values favor standard HOD models with no assembly bias parameters. Changes in 
the Bayesian Information Criterion $\vert \Delta \mathrm{BIC}\vert \ge 5$ strongly favor one model 
over another.
}
 }
 \label{table:priors}
 \end{center}
\end{table}
%--------------------------------------------------------------------------------------------------------------------------------
